Unified Understanding of the Dielectric Nature of Two-Dimensional Materials

### 2018-10-30 paper.tex
Change the order for 2D-3D transition part

Apart from the universal Moss-like relations we propose for the
dielectric nature of 2D materials, it is also of high theoretical
interest to model the 2D-3D transition of dielectric properties. In
other words, can we describe the dielectric constants
$\varepsilon^{\parallel}_{\mathrm{Bulk}}$ and
$\varepsilon^{\perp}_{\mathrm{Bulk}}$ of a bulk layered material from
$\alpha^{\parallel}$ and $\alpha^{\perp}$ of the monolayer (see Figure
\ref{fig-4}a)? First, we see that the 2D polarizabilities for
individual layers in the bulk materials
$\alpha_{\mathrm{Bulk}}^{\parallel}$ and
$\alpha_{\mathrm{Bulk}}^{\perp}$, can be calculated using
Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}, when $L$
becomes the bulk interlayer distance $L_{\mathrm{Bulk}}$. The
dielectric constants of the bulk material are then expressed as:
\begin{subequations}
\begin{eqnarray}
  \label{eq:3D-para}
  &\varepsilon^{\parallel}_{\mathrm{Bulk}} &= 1 + {\displaystyle \frac{\alpha_{\mathrm{bulk}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}}}\\
  \label{eq:3D-perp}
  &\varepsilon^{\perp}_{\mathrm{Bulk}} &= \left(1 - \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
\end{eqnarray}
\end{subequations}
Note that $\alpha_{\mathrm{Bulk}}^{\parallel}$ and
$\alpha_{\mathrm{Bulk}}^{\perp}$ may not essentially be the same as
$\alpha$ of isolated layer, but still quite close as seen in Figure
\ref{fig-3}b and \ref{fig-3}c. Nevertheless we will first see how good
we can predict $\varepsilon_{\mathrm{Bulk}}^{\parallel}$ and
$\varepsilon_{\mathrm{Bulk}}^{\perp}$, when assuming
$\alpha_{\mathrm{bulk}}=\alpha$. We compare
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ and
$\varepsilon_{\mathrm{bulk}}^{\perp}$ from first principles DFT
calculations compared with the values predicted using Eqs
\ref{eq:3D-para} and \ref{eq:3D-perp}, as show in Figure \ref{fig-4}b
and \ref{fig-4}c, respectively. Data calculated at both HSE06 and PBE
levels which give almost identical trends, indicating the generality
of such approach. Note although the stacking order is not considered
in Eqs. \ref{eq:3D-para} and \ref{eq:3D-perp}, we found that the
influence of stacking is minor (see Supplementary Figure SXX
\todo{Wait for Declan's data}). We observe that the majority of
predicted $\varepsilon_{\mathrm{bulk}}^{\parallel}$ values align along
the line $y=x$ , with a linear regression slope of 1.01 and $R^2$ of
0.97, indicating that such method indeed captures the transition from
$\alpha^{\parallel}$ to $\varepsilon_{\mathrm{Bulk}}^{\parallel}$. On
the other hand, we observe the predicted values of
$\varepsilon_{\mathrm{bulk}}^{\perp}$ has good agreement with the DFT
values when $E_{\mathrm{g}}>4$ eV, while the deviation becomes larger
when $E_{\mathrm{g}}$ reduces. The difference for the prediction of
$\varepsilon^{\parallel}$ and $\varepsilon^{\perp}$ means that
$\alpha^{\parallel}_{\mathrm{Bulk}}$ can generally be estimated from
its 2D counterpart, while $\alpha^{\perp}_{\mathrm{Bulk}}$ differs due
to interlayout coupling and overlap between induced dipoles, as also
observed in Figure \ref{fig-3}b, \ref{fig-3}c, and other studies
\cite{Andersen_2015_dielec_vdWH,Laturia_2018}. With a better model
describing $\alpha_{\mathrm{bulk}}^{\perp}$ as function of
$\alpha^{\perp}$ and the degree of interlayer coupling \cite{Tkatchenko_2012}, the dielectric transition from 2D to 3D would
be smoothly described.

@@

\todo[inline]{I have some doubt how to handle the next paragraph, keep the status quo}
As described in the previous section, the 2D Moss-like relation
between $\alpha^{\parallel}$ and $E_{g}$ is similar to the 3D Moss
relation between $\varepsilon$ and $E_{g}$, with a different power
law. Such difference in the power law can indeed be explained by
modern theory of dielectric properties.  Extend the approach
Eq. \ref{eq:alpha_perp_RPA} to the bulk material, and use the Bloch
presentation for wavefunctions in all dimensions, we derive (detailed
procedure see Supplementary Section S4):
\begin{equation}
  \label{eq:alpha-Eg-3D}
  \begin{aligned}[t]
  \varepsilon_{\mathrm{bulk}} &= 1 + \frac{2e^{2}}{\varepsilon_{0}(2\pi)^{3}}\int d^{3}\mathbf{k}
  \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(k)>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})} \\
  &\propto E_{g}^{-\frac{1}{2}},\ \mathrm{when}\ \varepsilon_{\mathrm{Bulk}} \gg 1
\end{aligned}
\end{equation}
which recovers the 3D Moss relation. Therefore, the universal
$\alpha^{\parallel}-E_{\mathrm{g}}$ relation is indeed the Moss
relation in 2D world, while the power law of $E_{\mathrm{g}}$ and
independence of effective mass is a result of the confinement
perpendicular to the 2D plane.

>>>>

The universal Moss-like relation shown in the previous sections
provides general understanding of the dielectric nature of 2D
materials. Moreover, the underlying physical mechanism allows us to
further bridge the 2D and 3D dielectric and electronic properties. As
described in the previous section, the 2D Moss-like relation between
$\alpha^{\parallel}$ and $E_{g}$ is similar to the 3D Moss relation
between $\varepsilon$ and $E_{g}$, with a different power law. Such
difference in the power law can indeed be explained by modern theory
of dielectric properties.  Extend the approach
Eq. \ref{eq:alpha_perp_RPA} to the bulk material, and use the Bloch
presentation for wavefunctions in all dimensions, we derive (detailed
procedure see Supplementary Section S4):
\begin{equation}
  \label{eq:alpha-Eg-3D}
  \begin{aligned}[t]
  \varepsilon_{\mathrm{bulk}} &= 1 + \frac{2e^{2}}{\varepsilon_{0}(2\pi)^{3}}\int d^{3}\mathbf{k}
  \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(k)>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})} \\
  &\propto E_{g}^{-\frac{1}{2}},\ \mathrm{when}\ \varepsilon_{\mathrm{Bulk}} \gg 1
\end{aligned}
\end{equation}
which recovers the 3D Moss relation. Therefore, the universal
$\alpha^{\parallel}-E_{\mathrm{g}}$ relation is indeed the Moss
relation in 2D world, while the power law of $E_{\mathrm{g}}$ and
independence of effective mass is a result of the confinement
perpendicular to the 2D plane.

The relation between 2D polarizability and 3D dielectric constant
shown in Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def} can
be further used to reconstruct the dielectric
constants $\varepsilon^{\parallel}_{\mathrm{Bulk}}$ and
$\varepsilon^{\perp}_{\mathrm{Bulk}}$ of a bulk layered material from
$\alpha^{\parallel}$ and $\alpha^{\perp}$ of the monolayer (see Figure
\ref{fig-4}a). First, we see that the 2D polarizabilities for
individual layers in the bulk materials
$\alpha_{\mathrm{Bulk}}^{\parallel}$ and
$\alpha_{\mathrm{Bulk}}^{\perp}$, can be calculated using
Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}, when $L$
becomes the bulk interlayer distance $L_{\mathrm{Bulk}}$. The
dielectric constants of the bulk material are then expressed as:
\begin{subequations}
\begin{eqnarray}
  \label{eq:3D-para}
  &\varepsilon^{\parallel}_{\mathrm{Bulk}} &= 1 + {\displaystyle \frac{\alpha_{\mathrm{bulk}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}}}\\
  \label{eq:3D-perp}
  &\varepsilon^{\perp}_{\mathrm{Bulk}} &= \left(1 - \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
\end{eqnarray}
\end{subequations}
Note that $\alpha_{\mathrm{Bulk}}^{\parallel}$ and
$\alpha_{\mathrm{Bulk}}^{\perp}$ may not essentially be the same as
$\alpha$ of isolated layer, but still quite close as seen in Figure
\ref{fig-3}b and \ref{fig-3}c. Nevertheless we will first see how good
we can predict $\varepsilon_{\mathrm{Bulk}}^{\parallel}$ and
$\varepsilon_{\mathrm{Bulk}}^{\perp}$, when assuming
$\alpha_{\mathrm{bulk}}=\alpha$. We compare
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ and
$\varepsilon_{\mathrm{bulk}}^{\perp}$ from first principles DFT
calculations compared with the values predicted using Eqs
\ref{eq:3D-para} and \ref{eq:3D-perp}, as show in Figure \ref{fig-4}b
and \ref{fig-4}c, respectively. Data calculated at both HSE06 and PBE
levels which give almost identical trends, indicating the generality
of such approach. Note although the stacking order is not considered
in Eqs. \ref{eq:3D-para} and \ref{eq:3D-perp}, we found that the
influence of stacking is minor (see Supplementary Figure SXX
\todo{Wait for Declan's data}). We observe that the majority of
predicted $\varepsilon_{\mathrm{bulk}}^{\parallel}$ values align along
the line $y=x$ , with a linear regression slope of 1.01 and $R^2$ of
0.97, indicating that such method indeed captures the transition from
$\alpha^{\parallel}$ to $\varepsilon_{\mathrm{Bulk}}^{\parallel}$. On
the other hand, we observe the predicted values of
$\varepsilon_{\mathrm{bulk}}^{\perp}$ has good agreement with the DFT
values when $E_{\mathrm{g}}>4$ eV, while the deviation becomes larger
when $E_{\mathrm{g}}$ reduces. The difference for the prediction of
$\varepsilon^{\parallel}$ and $\varepsilon^{\perp}$ means that
$\alpha^{\parallel}_{\mathrm{Bulk}}$ can generally be estimated from
its 2D counterpart, while $\alpha^{\perp}_{\mathrm{Bulk}}$ differs due
to interlayout coupling and overlap between induced dipoles, as also
observed in Figure \ref{fig-3}b, \ref{fig-3}c, and other studies
\cite{Andersen_2015_dielec_vdWH,Laturia_2018}. With a better model
describing $\alpha_{\mathrm{bulk}}^{\perp}$ as function of
$\alpha^{\perp}$ and the degree of interlayer coupling \cite{Tkatchenko_2012}, the dielectric transition from 2D to 3D would
be smoothly described.

@@
